---
title: "Multiple Imputation"
author: "Linxi Li T00622714"
date: "2022-10-20"
output: pdf_document
---

This instruction is for imputation missing data
We are using mice() package to deal with the missing data
So we installed the package


```{r}
#install.packages("mice")
```

```{r}
library(mice)
library(VIM)
```

# R Markdown
I created a dataset and save as a csv document:

```{r cars}
data <- read.csv("/Users/ccc/Desktop/create data.csv")
data
```

# Including Plots
I am going to show the plot of how the data missing, the red spot represents
the missing data


```{r}
md.pattern(data)
md.pairs(data)
```


We can also draw the data distribution of each column of the data set. 


In the figure, the red color indicates the missing values, and the transition 
colors from black to gray to white indicate the different values, the more 
transition colors indicate the more scattered data values, and the less 
transition colors indicate the more concentrated data values.


```{r}
matrixplot(data)
```

Next, we use the mice() function, which is used to populate the data

```{r}
imputed_Data <- mice(data, m=10, maxit = 5, method = 'pmm', seed = 500)

#note that: 
#m, the number of fill matrices for the multi-fill method, default is 5
#maxit, the maximum number of iterations, default is 5
#method, the method used to fill, and pmm is predictive mean matching.
#We can use methods(mice) to see what methods are available.
```

```{r}
summary(imputed_Data)
```

# View the result of imputation:

```{r}
imputed_Data$imp
```

View the plot of Sub-panel observations, grouped by independent individual 
indicators, were populated for the 10 groups of data.


```{r}
stripplot(imputed_Data, col=c("grey",mdc(2)),pch=c(1,20))
```


# Analyze the results and optimize the model

```{r}
fit=with(imputed_Data,lm(Ozone ~ Wind + Solar.R + Temp))
summary(fit)
```

Using the with() function, a multiple linear regression analysis model was 
performed on the five interpolated data sets, and a t-test was performed to 
determine the validity of each variable in the data set.


```{r}
pooled=pool(fit)
pool.r.squared(fit)
```



```{r}
completeData1 <- complete(imputed_Data,1)
data1 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData1)
summary(data1)
```

```{r}
completeData2 <- complete(imputed_Data,2)
data2 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData2)
summary(data2)
```

```{r}
completeData3 <- complete(imputed_Data,3)
data3 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData3)
summary(data3)
```

```{r}
completeData4 <- complete(imputed_Data,4)
data4 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData4)
summary(data4)
```

```{r}
completeData5 <- complete(imputed_Data,5)
data5 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData5)
summary(data5)
```

```{r}
completeData6 <- complete(imputed_Data,6)
data6 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData6)
summary(data6)
```

```{r}
completeData7 <- complete(imputed_Data,7)
data7 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData7)
summary(data7)
```

```{r}
completeData8 <- complete(imputed_Data,8)
data8 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData8)
summary(data8)
```

```{r}
completeData9 <- complete(imputed_Data,9)
data9 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData9)
summary(data9)
```

```{r}
completeData10 <- complete(imputed_Data,10)
data10 <- lm(Ozone ~ Wind + Solar.R + Temp, data=completeData10)
summary(data10)
```

By checking the R-square, I am going to use the imputation 8, as our missing data. 
So our model will be: Ozone = 40.23805-1.70001Wind-0.02226Solar.R+0.17566Temp


# Distribution of 100 imputation
```{r}
imputed_Data100 <- mice(data, m=100, maxit = 5, method = 'pmm', seed = 500)
fit100=with(imputed_Data100,lm(Ozone ~ Wind + Solar.R + Temp))
summary(fit100)
```


```{r}
d = matrix(nrow = 100, ncol = 4)
for (i in seq(1,100)){
  for (j in seq(1,4)){
    d[i,j]=fit100$analyses[[i]][[1]][[j]]
    #print(i)
  }
}
d
hist(d[,1],breaks=50,xlab="Intercept", ylab="distribution",main="Intercept Density",
     col = "brown")
hist(d[,2],breaks=50,xlab="Wind", ylab="distribution",main="Wind Density",
     col="orange red")
hist(d[,3],breaks=50,xlab="Solar.R", ylab="distribution",main="Solar R Density",
     col="lime green")
hist(d[,4],breaks=50,xlab="Temp", ylab="distribution",main="Temperature Density",
     col="medium slate blue")
```


